Postural developments mediate children's visual access to social information

### 2018-01-25 writeup-cogsci/cogsci2018_faceOnly.Rmd
glm/glmer model details

@@

# Changes in Access to Faces 
```{r detByAge, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3, fig.height=2, fig.cap = "Proportion of faces detected by the MTCNN model (left) and wrists detected by the OpenPose model (right panel) as a function of child's age. Larger dots indicate children who had longer playsessions and thus for whom there was more data"}
detectionsByAge <- dlong %>%
  filter(!is.na(age.at.test)) %>%
  group_by(subid, age.at.test, detectorType) %>%
  summarise(detections = mean(detection)) %>%
  left_join(inc_subs) %>%
  mutate(len = as.numeric(len.min))

ggplot(detectionsByAge, aes(x = age.at.test, y = detections, color = detectorType, size=len.min)) +
    geom_jitter(width = .25) +
    geom_smooth(size=1) +
    scale_x_continuous(breaks=c(8,12,16)) +
    scale_size_continuous(range=c(.01,2),name = "Video Length (mins)") +
    labs(y = "Prop. detected", x = element_blank()) +
    theme_few() + 
    theme(legend.position="none") +
    facet_grid(~detectorType, scales = "free_y") 
```

@@

dlongPlot <-dlong %>%
    filter(detectorType!="OpenPose-Faces")

@@

p2=ggplot(detectionsByOrientation, aes(x = factor(age.grp), y = detections, col = orientation)) + 
  geom_boxplot(outlier.size = 0.5) + 
  labs(y = "Prop. detected", x = element_blank()) +
  facet_grid(~detectorType, scales="free_y") +
  theme_few() +
  theme(legend.position="right", legend.text=element_text(size = 8), legend.margin=margin(t=0, r=0, b=0, l=0, unit="cm")) +

@@

```{r echo=FALSE, include=FALSE}
d$faceNum_MT=as.numeric(d$faceMT)
d$faceNum_OP=as.numeric(d$faceOP)

@@

@@

fullModelminsInt_Faces_OP <- glm(faceNum_OP ~ scale(age.at.test) + posture + orientation,
       data = d,
       family = "binomial")

>>>>

# Function to evaluate detectors
evaluate <- function(a, b) {
  if (a == TRUE) {
    if (a == b) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (a == b) return("TN") # was not face/wrist, detected face/wrist
    else return("FP") # was not face/wrist, said face/wrist
  }
}

@@

# Changes in Access to Faces 
```{r detByAge, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3, fig.height=2, fig.cap = "Proportion of faces detected by the MTCNN model (left) and wrists detected by the OpenPose model (right panel) as a function of child's age. Larger dots indicate children who had longer playsessions and thus for whom there was more data"}
detectionsByAge <- dlong %>%
  filter(detectorType!="OpenPose-Faces") %>% # for brevity
  filter(detectorType!="ViolaJones-Faces") %>% # low performance
  filter(!is.na(age.at.test)) %>%
  group_by(subid, age.at.test, detectorType) %>%
  summarise(detections = mean(detection)) %>%
  left_join(inc_subs) %>%
  mutate(len = as.numeric(len.min))

ggplot(detectionsByAge, aes(x = age.at.test, y = detections, color = detectorType, size=len.min)) +
    geom_jitter(width = .25) +
    geom_smooth(size=1) +
    scale_x_continuous(breaks=c(8,12,16)) +
    scale_size_continuous(range=c(.01,2),name = "Video Length (mins)") +
    labs(y = "Prop. detected", x = element_blank()) +
    theme_few() + 
    theme(legend.position="none") +
    facet_grid(~detectorType) 
```

@@

dlongPlot <-dlong %>%
    filter(detectorType!="OpenPose-Faces") %>%
    filter(detectorType!="ViolaJones-Faces")

@@

p2=ggplot(detectionsByOrientation, aes(x = factor(age.grp), y = detections, col = orientation)) + 
  geom_boxplot(outlier.size = 0.5) + 
  labs(y = "Prop. detected", x = element_blank()) +
  facet_grid(~detectorType, scales="free_y") +
  theme_few() +
  theme(legend.position="right", legend.text=element_text(size = 8), legend.margin=margin(t=0, r=0, b=0, l=0, unit="cm"))

@@

```{r echo=FALSE, include=FALSE}

## First try a normal logistic regressino, grouping by subject / posture / orientation
# wrangle data
dModelGLM <- d %>%
  group_by(subid, posture, orientation) %>%
  summarize(countDetected=sum(faceMT==TRUE), countTotal = sum(faceMT==FALSE), age.at.test=age.at.test[1])
y=cbind(dModelGLM$countDetected, dModelGLM$countTotal) # successes / failures for modeling proportions
dModelGLM$age.at.test=scale(dModelGLM$age.at.test) # scale and center continous predictor
# run model
normalGLM<-glm(y ~ dModelGLM$age.at.test + dModelGLM$posture + dModelGLM$orientation,family=binomial(logit))
# output results
normalGLM <- normalGLM %>%
  xtable %>%
  print(type="latex", comment = F, table.placement = "H")

# Then fit a mixed effet model
fullModel <- glmer(faceMT ~ scale(age.at.test)+(posture)+(orientation) + (1|subid),
       data = d,
       family = "binomial")

@@

 <- glm(faceNum_MT ~ scale(age.at.test) + posture + orientation,
       data = d,
       family = "binomial")

@@
